---
title: "We are better than you? REF edition"
author:
  - name: Frank Popham
date: 2022-05-12
output:
  distill::distill_article:
    self_contained: false
---

The [research excellence framework](https://www.ref.ac.uk/) represents another opportunity for universities in the UK to boast they are better than their peers. [In this article](https://www.timeshighereducation.com/campus/dont-let-ref-tail-wag-academic-dog) Marcus Manufò highlighted how Glasgow had pre-registered that they

> will focus on collegiality over superiority, avoiding unnecessary comparisons and presenting the results
> as evidence of Glasgow's significant contribution to the collaborative research endeavour.

As a first check I scraped every REF result related tweet from the main account of [Russell Group universities](https://www.russellgroup.ac.uk/) on the 12th May 2022 up to midday. These are 24 "leading" universities. They are republished below by university. I have tried to exclude non-relevant tweets and also retweets. Exeter and Nottingham's accounts had not tweeted anything about REF results by noon.

Make your own mind up about how Glasgow compares in its tweets to the others. I thought there was less comparison than I was expecting.

The code to reproduce the analysis is [here](https://github.com/frankpopham/reftweet). Thanks to [R](https://www.r-project.org/), [Rstudio](https://www.rstudio.com/), [tidyverse](https://www.tidyverse.org/), [rtweet](https://docs.ropensci.org/rtweet/), [tweetrmd](https://github.com/gadenbuie/tweetrmd) for making this easy to do and [distill](https://rstudio.github.io/distill/) for making the blog easy to produce.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
library(rvest)
library(rtweet)
library(tweetrmd)

#get list of russell group unis

rus_web <-read_html("https://russellgroup.ac.uk/about/our-universities/")
rus_web2 <- rus_web %>%
  html_elements(".header_our_uni_dropdown") %>%
  pluck(1) %>%
  html_elements("a") 

rus_web_df <- 
  tibble(name=rus_web2 %>% html_text2(),
         url=rus_web2 %>% html_attr("href")) %>%
  mutate(url=paste0("https://russellgroup.ac.uk", url))

#get uni website

rus_web3<-rus_web_df$url %>%
  map(read_html) %>%
  map(~html_elements(.x, ".uni_box")) %>%
  map(~html_elements(.x, "a")) %>%
  map(~pluck(.x, 1)) 


rus_web_df <- rus_web_df %>%
  mutate(url2=rus_web3 %>% map(~html_attr(.x, "href"))) %>%
  mutate(url2=str_replace(url2, "http", "https")) %>%
  mutate(url2=str_replace(url2, "httpss", "https"))

#having problems with warwick not returning data so exclude
  
rus_web4 <- rus_web_df %>%
  filter(name!="University of Warwick") 

#get uni pages, could do analysis of these

rus_web5 <- rus_web4$url2 %>%
  map(read_html)  

names(rus_web5) <- rus_web4$name

#tweets 
#get twitter handles


rus_web6 <- as.list(rus_web_df$name)
names(rus_web6) <- rus_web_df$name

rus_tweet <- rus_web6 %>%
  map_dfr(~search_users(.x, n=1)) %>%
  mutate(screen_name=if_else(screen_name=="UoNSU", "UniofNottingham", screen_name))

#get latest tweets

rus_web7 <- as.list(rus_tweet$screen_name)
names(rus_web7) <- rus_web_df$name

rus_tweet2 <- rus_web7 %>%
  map_dfr(~get_timeline(.x, n=20))

#keep tweets from 12th May (Ref results day) - I looked at tweets b4 midday

rus_tweet2 <- rus_tweet2 %>%
  mutate(tday=date(created_at)) %>%
  filter(tday=="2022-05-12") %>%
  mutate(thour=hour(created_at)) %>%
  filter(thour < 12) %>%
  filter(is_retweet==FALSE) %>%
  filter(status_id!="1524671472408698883" &
         status_id!="1524671470139547648" &
         status_id!="1524671474841313281" &
         status_id!="1524671480482643969" &
         status_id!="1524671483729092611" &
         status_id!="1524671486468014080" &
         status_id!="1524706090671382532" &   
         status_id!="1524665887189614593" &
         status_id!="1524656070660083712" &
         status_id!="1524666211363086337" &  
         status_id!="1524669039024484352" &
         status_id!="1524697938420715520" &
         status_id!="1524677693421330432" &
         status_id!="1524678159400148993" &
         status_id!="1524678477856788481" &   
         status_id!="1524648999608889347" &
         status_id!="1524689806931939329" &
         status_id!="1524704190555213825" &   
         status_id!="1524687578380832769" &
         status_id!="1524711994493964289" & 
         status_id!="1524691100010790914" &
         status_id!="1524703962854789123" &
         status_id!="1524696384724783105" &
         status_id!="1524692577789829121" &  
         status_id!="1524660919820767233" & 
         status_id!="1524687578380832769" & 
         status_id!="1524697938420715520" &
         status_id!="1524711994493964289" &
         status_id!="1524713507480088576" &
         status_id!="1524717357276569600" &
         status_id!="1524717365191135238" &
         status_id!="1524717371004436481" &  
         status_id!="1524717377790910464" &  
         status_id!="1524717380944936960" & 
         status_id!="1524717357276569600") %>%
  group_by(screen_name) %>%
  arrange(created_at, .by_group=TRUE)

 
```

```{r tweets}



htmltools::tagList(
  map(rus_tweet2$status_url, ~tweet_embed(.x, plain=TRUE))
)







```
